\section{Group Members Contribution}

\begin{description}
    \item[Everyone] has contributed in the project by sharing ideas, suggestions and fixing issues in a proactive way. We all took part in the analyses process and decided to split the development of some parts of the project equally (DAOs, Servlets, jsps, ...).
    \item[Alessandro Borsato] has developed part of the registration process, proposed a common approach to manage the project (ticketing and git) and wrote internal guides to let everyone aligned.
    \item[Andrea Campagnol] has contributed to this project by taking care of some initial setups, developing the login and mail verification parts. He also draw the main schemas present in this document.
    \item[Vittorio Cardillo] has helped the team in the initial setup and developed some key parts like the homepage. Has also made the first graphic design of the application and implementation of resources.
    \item[Vaidas Lenartavicius] has developed user edit page and several others parts of this project. He was always available support teammembers in case of fixing bug and problems.
    \item[Mattia Maglie] helped during the design of the project with requirements, definitions of DAOs and Entity-Relationship diagram. Developed some DAOs regarding events, and servlets with respective jsp. He took care of the payment section of the app and developed attribute insertion logic and filters. Also he suggested some useful refactoring of the code and best practices.
    \item[Francesco Marcato] has proposed the idea for this application, as a result of a practical need in Padua ESN management. He wrote the requirements of this application and wrote code mainly for the events part.
    \item[Laura Pallante] has contributed to the project by implementing some key pages and structuring REST architecture on some of those. She was also helpful in case of fixing some issues.
    \item[Md Imran Faruck Talukder] has contributed to the project by taking care of the database implementation, also helping teammates setting up the connection between the application and db.
    \item[Matteo Villani] has developed some filter parts and edit pages. He took care of aligning the style of the app pages.
    \item[Giovanni Zago] has set up the Trello application we used to divide the work among us, also providing a simple tutorial on how to use it properly. He took care of writing most of the parts in the documentation (included pages mockups) and also some application pages, s.e. editing users information as user or as administrator.
\end{description}